%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[overlapped, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage[margin=0.5in]{geometry}
%\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

%\addtolength{\oddsidemargin}{-.875in}
%\addtolength{\evensidemargin}{-.875in}
%\addtolength{\textwidth}{1.75in}
%
%\addtolength{\topmargin}{-.875in}
%\addtolength{\textheight}{1.75in}
\setlength{\textwidth}{7in} % Text width of the document

\begin{document}

\begin{resume}
%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Danny Chen} % Your name at the top
 
    \moveleft\hoffset\vbox{\hrule width 7.5in height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{+1 512 629 0747}
\moveleft.5\hoffset\centerline{dannychen579@utexas.edu}

%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
%\section{OBJECTIVE}  
%Looking for a job as a software developer. I have a keen interest in cryptography, networking, and algorithms
%

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}


{\sl Bachelor of Science in Computer Science}  \hfill {\sl 2012-08/2016-05} \\
University of Texas at Austin
\\
Coursework: Operating Systems, Cryptography, Algorithms, Network Security, Artificial Intelligence, Automata Theory, Theory of Computation

 
%----------------------------------------------------------------------------------------
%   TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNICAL SKILLS AND KNOWLEDGE} 
{\sl Languages:} C, Bash, Python, x86 Assembly, Java, Javascript, Golang, Ruby\\
{\sl Technologies/Tools:} Amazon EC2, Amazon VPC, Git, Travis CI\\
{\sl Operating Systems:} Linux
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

{\sl Software Development Engineer II} \hfill {\sl 2016-07-05/Present} \\
EC2 Networking, Amazon Web Services
\begin{itemize} \itemsep -2pt % Reduce space between items
    \item Worked as part of a team that performs routing and packet translation for all network traffic going in and out of EC2 worldwide.
    \item Worked on and maintained a low-level packet processing application written in C.
    \item Implemented the network security layer for Inter-Region VPC Peering.
    \item Worked on a 24/7 oncall shift to troubleshoot hardware and software failures in production.
    \item Designed and oversaw projects to improve operational overhead and alleviate technical debt, often in conjunction with other teams in AWS.
\end{itemize}
{\sl Software Development Engineer Intern} \hfill {\sl 2015-07-02/2015-08-28} \\
Platform Excellence, Amazon.com
\begin{itemize} \itemsep -2pt % Reduce space between items
    \item Worked as part of the team that monitors latency on the Amazon.com website.
    \item Created a data visualization tool for a terabyte-scale Redshift cluster.
\end{itemize}
{\sl Software Developer Intern} \hfill {\sl 2014-07-02/2014-08-27} \\
Software Verification Team for WebSphere Application Server, IBM
\begin{itemize} \itemsep -2pt % Reduce space between items
    \item QA and tested IBM WebSphere.
    \item Wrote scripts to do automated testing of new releases of Websphere.
\end{itemize}
 

%----------------------------------------------------------------------------------------
%	Personal Side Projects
%---------------------------------------------------------------------------------------- 

\section{PERSONAL PROJECTS}
{\sl Minecraft Client} - https://github.com/NosotrosNueces/mcc
\begin{itemize} \itemsep -2pt % Reduce space between items
    \item Collaborated with friends to implement the Minecraft Client protocol.
    \item Provides an API for sending commands to the server like digging and moving.
    \item Allows for asynchronous handling of messages from the server through user-specified callbacks. Backed by libuv, the same library that handles asynchronous I/O for Node.js.
    \item Implemented simple bots that can break blocks, attack enemy entities, and build structures.
\end{itemize}
{\sl Gameboy Emulator} - https://github.com/mukkid/GoBoy
\begin{itemize} \itemsep -2pt % Reduce space between items
    \item An active collaborative project with a friend to implement software emulation of the Gameboy console.
    \item Completed full emulation of the Z80 CPU
    \item Adopted and enforced test-driven development and CI practices.
\end{itemize}
{\sl Chess AI} - http://github.com/SrsBusiness/Party
\begin{itemize} \itemsep -2pt % Reduce space between items
    \item Game state is represented using bitboards and transitions between states are implemented efficiently with bitwise operations and table lookups.
    \item Uses AI techniques such as alpha-beta pruning, transpositional hash tables, and iterative deepening.
\end{itemize}
{\sl Fast Fourier Transform} - http://github.com/SrsBusiness/FFT
\begin{itemize} \itemsep -2pt % Reduce space between items
    \item A minimal implementation of the Cooley-Tukey algorithm to compute discrete Fourier transforms.
\end{itemize}

\end{resume}
\end{document}
